PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-11-18 qfenv_paper/qf_environment.tex
primus group edits part 1
Partially address comments by Guangtun, Ramin, and Alison.
Updated most of the figures to new aperture size.

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
John Moustakas\altaffilmark{2},
Alison~Coil\altaffilmark{3}, 
Richard~Cool\altaffilmark{4}, 
Daniel Eisenstein\altaffilmark{5},
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRism MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited Environment
Defining Population (from PRIMUS and SDSS). For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
star formation only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on
the evolution of the quiescent fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\cite{York:2000aa}).

@@

\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:masscomp}
From the low redshift SDSS-{\em GALEX} and intermediate redshift
PRIMUS data we define our mass complete galaxy
sample. We begin by imposing the parent sample selection criteria from
\cite{Moustakas:2013aa}. More specifically, we take the statistically
complete {\em primary} sample from the PRIMUS data
(\citealt{Coil:2011aa}) and impose magnitude limits on optical
selection bands as specified in \cite{Moustakas:2013aa} Table 1. These
limits are in different optical selection bands and have distinct
values for the five PRIMUS target fields. We then exclude stars and
broad-line AGN to only select objects spectroscopically classified as
galaxies, with high-quality spectroscopic redshifts ($Q \geq
3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the
PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations
from sample variance and $ z < 0.8$ is selected due to the lack of
sufficient statistics in subsamples defined below.

@@

%We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY ENVIRONMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments. We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}

\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it. We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.

For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} =
\apradius\;
\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$.  We use a
cylindrical aperture in order to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). \cite{Cooper:2005aa} finds that $\pm 1000 \; \rm{km} \;
\rm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our aperture height choice of
$\apheight\;
\rm{Mpc}$ accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=0}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments in the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \rm{Mpc}$ and $H=\apheight \: \rm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\:
\mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\rm{log}
  \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log}
  \:\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (following \citealt{Moustakas:2013aa}). For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time. For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular RA and Dec grid and calculate the SMFs after excluding one grid at a time. From the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{M-1}{M} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$M$ in this equation is the number of jack knife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jack knife $\Phi^j$s.

@@

In addition to the evolution over cosmic time, we observe noticeable
trends when we compare the SMFs for star-forming and quiescent
galaxies between the two environments. Comparison of the SMFs in low
versus high density environments reveal a noticeable relation between
mass and density, with SMFs in high density environments having more
massive galaxies. We further confirm this trend when we compare the
median mass between the two environments to find that the median mass
for galaxies in high density environments is significantly greater
than in low density environments. The relationship between mass and
environment observed in our SMFs reflects the well-established
mass-density relation and observed mass segregation with environment
in the literature (\citealt{norberg02a, zehavi02a, Blanton:2005ab,
  bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).

>>>>

\title{PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$}
\author{
ChangHoon~Hahn\altaffilmark{1}, 
Michael~Blanton\altaffilmark{1}, 
John Moustakas\altaffilmark{2},
Alison~Coil\altaffilmark{3}, 
Richard~Cool\altaffilmark{4}, 
Daniel Eisenstein\altaffilmark{5},
Ken Wong\altaffilmark{6}, 
Guangtun Zhu\altaffilmark{7}
}
\altaffiltext{1}{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003}
\altaffiltext{2}{Department of Physics and Astronomy, Siena College, 515 Loudon Road, Loudonville, NY 12211}
\altaffiltext{3}{Center for Astrophysics and Space Sciences, Department of Physics, University of California, 9500 Gilman Dr., La Jolla, CA 92093}
\altaffiltext{4}{MMT Observatory, University of Arizona, 1540 E Second Street, Tucson AZ 85721}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\altaffiltext{6}{Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721} 
\altaffiltext{7}{Department of Physics and Astronomy, The Johns Hopkins University, 3400 North Charles Street, Baltimore, MD 21218} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We investigate the effects of galaxy environment on the evolution of
the quiescent fraction ($f_{\rm{Q}}$) from $z =0.8 $ to $ 0.0$ using
spectroscopic redshifts and multi-wavelength imaging data from the
PRIsm MUlti-object Survey (PRIMUS) and the Sloan Digitial Sky Survey
(SDSS). Our stellar mass limited galaxy sample consists of $\sim
13,000$ PRIMUS galaxies within $z = 0.2-0.8$ and $\sim 64,000$ SDSS
galaxies within $z = 0.05-0.12$. We classify the galaxies as quiescent
or star-forming based on an evolving specific star formation cut, and
as low or high density environments based on fixed cylindrical
aperture environment measurements on a volume-limited environment
defining population (from PRIMUS and SDSS). For quiescent and
star-forming galaxies in low or high density environments, we examine
the evolution of their stellar mass function (SMF). Then using the
SMFs we compute $f_{\rm{Q}}(\mathcal{M}_{*})$ and quantify its
evolution within our redshift range. We find that the quiescent
fraction is higher at higher masses and in denser environments. The
quiescent fraction rises with cosmic time for all masses and
environments. At a fiducial mass of $10^{10.5}M_\odot$, from $z\sim
0.7$ to $0.1$, the quiescent fraction rises by $15\%$ at the
lowest environments and by $25\%$ at the highest environments we measure.
These results suggest that for a minority of galaxies their cessation
of star formation is due to external influences on
them. However, in the recent Universe a substantial fraction of the
galaxies that cease forming stars do so due to internal processes.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% INTRODUCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Galaxies, in their detailed properties, carry the imprints of their
surroundings, with a strong dependence of the quiescent fraction of
galaxies on their local environment (e.g. \citealt{hubble36a,
oemler74a, dressler80a, hermit96a, guzzo97a}; for a recent review see
\citealt{blanton09a}).  The strength of this dependence is itself a
strongly decreasing function of galaxy stellar mass; at the extreme,
the lowest mass ($<10^{9}$ $M_\odot$) galaxies end their
star formation only in
dense regions, and never in isolation (\citealt{geha12a}).  These
effects vary with redshift at least in the densest clusters, as
observed in the changing fraction of late-type spirals relative to the
field found in studies of the morphology-density relation
(\citealt{dressler84a, desai07a}).  Clearly understanding the
properties of galaxies in the present-day universe requires a careful
investigation of the role of environment, and how that role changes
over time.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SAMPLE SELECTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sample Selection} \label{sec:sample}
We are interested in quantifying the effects of galaxy environment on
the evolution of the quiescent fraction over the redshift range $0 < z < 1$. For our analysis, we require a sample with sufficient depth and high quality spectroscopic redshift to probe the redshift range and to measure galaxy environment. PRIMUS with its $\sim 120,000$ spectroscopic redshifts provides a large data set at intermediate redshifts for our analysis. In addition, we anchor our analysis with a low redshift sample derived from the Sloan Digital Sky Survey (\citealt{York:2000aa}).

@@

\subsection{Stellar Mass Complete Galaxy Sample} \label{sec:target} 
From the low redshift SDSS-{\em GALEX} and intermediate redshift
PRIMUS data we define our mass complete galaxy
sample. We begin by imposing the parent sample selection criteria from
\cite{Moustakas:2013aa}. More specifically, we take the statistically
complete {\em primary} sample from the PRIMUS data
(\citealt{Coil:2011aa}) and impose magnitude limits on optical
selection bands as specified in \cite{Moustakas:2013aa} Table 1. These
limits are in different optical selection bands and have distinct
values for the five PRIMUS target fields. We then exclude stars and
broad-line AGN to only select objects spectroscopically classified as
galaxies, with high-quality spectroscopic redshifts ($Q \geq
3$). Lastly, we impose a redshift range of $ 0.2 < z < 0.8$ for the
PRIMUS galaxy sample, where $ z > 0.2$ is selected due to limitations
from sample variance and $ z < 0.8$ is selected due to the lack of
sufficient statistics in subsamples defined below.

@@

%We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY ENVIRONMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments. We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}

\subsection{Galaxy Environment} \label{sec:environment}
We define the environment of a galaxy as the number of neighboring Environment Defining Population galaxies (defined below) within a fixed aperture centered around it. We use a fixed aperture measurement of environment to quantify environment with an aperture sufficiently large to encompass massive halos (\citealt{Muldrew:2012aa, Skibba:2013aa}).
%We use a fixed aperture measurement of environment in order to probe environment on the halo scale, as \cite{Muldrew:2012aa} finds in their comparison of different environment definition using simulations.

For our aperture, we use a cylinder of dimensions: $R_{\rm{ap}} =
\apradius\;
\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$.  We use a
cylindrical aperture in order to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \rm{km} \;\rm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our aperture height choice of
$\apheight\;
\rm{Mpc}$ accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies in order to consistently measure environment throughout our entire sample, we note a significant discrepancy between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. We remind the reader that this is due to the different mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_smf_cylr2_50000h35_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_2envbin_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) target galaxies in 
low (left) and high (right) environments in the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \rm{Mpc}$ and $H=\apheight \: \rm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \rm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\rm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\rm{log}\: \mathcal{M}) \Delta(\rm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\rm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\rm{log}\:
\mathcal{M}) \Delta(\rm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\rm{log}
  \:\mathcal{M}, \rm{log} \:\mathcal{M}+\Delta(\rm{log}
  \:\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\rm{max,avail}}$ instead than $V_{\rm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

To calculate the uncertainty of the SMFs from the sample variance, we use a standard jackknife technique (following \citealt{Moustakas:2013aa}). For the PRIMUS galaxies, we calculate SMFs after excluding one of the five target fields at a time. For the SDSS target galaxies we divide the field into a 12 $\times$ 9 rectangular RA and Dec grid and calculate the SMFs after excluding one grid at a time. From the calculated SMFs we calculate the uncertainty: 
\begin{equation}
\sigma^j = \sqrt{\frac{N-1}{N} \sum\limits_{k=1}^{M} (\Phi^j_k - \langle \Phi^j \rangle)^2}
\end{equation} 
$N$ in this equation is the number of jackknife SMFs in the stellar mass bin. $\langle \Phi^j \rangle$ is the mean number density of galaxies in each stellar mass bin for all of the jackknife $\Phi^j$s.

@@

In addition to the evolution over cosmic time, we observe noticeable
trends when we compare the SMFs for star-forming and quiescent
galaxies between the two environments. Comparison of the SMFs in low
versus high density environments reveal a noticeable relation between
mass and density, with SMFs in high density environments having more
massive galaxies. We further confirm this trend w hen we compare the
median mass between the two environments to find that the median mass
for galaxies in high density environments is significantly greater
than in low density environments. The relationship between mass and
environment observed in our SMFs reflects the well-established
mass-density relation and observed mass segregation with environment
in the literature (\citealt{norberg02a, zehavi02a, Blanton:2005ab,
  bundy06a, Scodeggio:2009aa, Bolzonella:2010aa}).
